### 2013-04-17 article.tex
Make features clear at start of results
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>

Genomer was developed during our \emph{P. fluorescens} genome projects to
automate and simplify the manual steps required when finishing a microbial
genome. Genomer includes functions to simplify the following: updating and
modifying a genome sequence, editing genome annotations, and preparing the
required files to submit a draft or complete genome to a sequence database such
as GenBank. Genomer is also designed to allow researchers to add their own
functionality to a genome project through third-party plugins.

@@

\item{Sequencing reads are assembled into contigs with a high degree of
confidence. This is done by using various assembly software and testing
different software parameters \cite{earl2011}. The generated contigs are then
compared between assembly replicates using nucmer from the Mummer software
package \cite{kurtz2004}. The FASTA file of contig sequences are then added to
the Genomer project.}

\item{The assembled contigs are then annotated and the GFF3 file of contig
annotations is added to the Genomer project.}

@@

This allows the scaffold file to be continuously improved even when already
annotated. For instance, additional PCR sequences can be used to close gaps and
improve the genome sequence, without requiring reannotation or manually
updating all annotation coordinates.

@@

Generating a usable genome sequence requires sequencing, assembly of reads, and
annotation. A further step is also required: preparation of genomic files for
deposition in a database. An example is the GenBank database which requires the
genome annotations to be prepared in a custom table format. Additional files
are also required when the genome assembly is incomplete: a FASTA file
containing the individual contig sequences and `a golden path' (AGP)
\cite{agp-spec} file which describes the placement and direction of constituent
contigs in the draft genome sequence. The requirements to generate these
specific files can be time-consuming to complete and difficult to understand
for researchers new to field. We used Genomer extensively during our own genome
projects to simplify and automate this process.

>>>>

Genomer was developed during our \emph{P. fluorescens} genome projects to
automate and simplify the manual steps required when finishing a microbial
genome. Genomer provides the following functionality to facilitate this:

\begin{description}

  \item[Simple editting of a draft genome sequence.]{Genomer is built on the
  existing Scaffolder \cite{barton2012} file format for assembling a draft
  genome sequence. This YAML \cite{yaml} format simplifies the process of
  re-organising and trimming contigs in a draft genome without having to edit
  large nucleotide sequences manually.}

  \item[Simple mapping of annotations to the generated draft sequence.]{Genomer
  maps the coordinates of annotations on individual to repsective position in
  the draft genome sequence. This allows the scaffold file to be continuously
  improved even when already annotated. For instance, additional PCR sequences
  can be used to close gaps and improve the genome sequence, without requiring
  reannotation or manually updating all annotation coordinates.}

  \item[Generation of files for submission to GenBank.]{Submitting a genome
  sequence to GenBank database requires several specific files to be prepared.
  These may include a FASTA file of the draft sequence, a table of annotations,
  a FASTA file containing the individual contig sequences, and `a golden path'
  (AGP) \cite{agp-spec} file describing the placement of contigs. Genomer
  automates the generation of all these files.}

  \item[Integration with the command line.]{Genomer is built as a command line
  tool built around plain text files following the Linux philosophy. This
  allows for integration with tools such as GNU Make or git, and also to allow
  reproducible scripting of the process of finishing a genome.}

\end{description}

@@

\item{A genomer project is organised around a set of already assembled and
annotated contigs. For example we assemble our contigs using the A5 pipeline
\cite{tritt2012} and and then subsequently annotate them using the Integrated
Microbial Genomes resource \cite{markowitz2006}. We then use these contigs as a
starting point to build a draft genome sequence in genomer.}

@@

@@
